Tor's Usability for Censorship Circumvention

### 2015-10-05 paper/circumvention-experiment.tex
linked correct .bib file
made the tasks fit into one line

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item Do a Google web search for the population of Zimbabwe. 
\item On Youtube, find a video playing Bach's ``Ode to Joy.'' 
\item Find the Amazon best-sellers in the ``Movies \& TV'' category.
\item On Yahoo, find the exchange rate between dollars and euros.
\item In the Wikipedia ``History'' portal, click on the featured article. 
\item On Twitter, find the currently trending topics.
\item On Bing Maps, find directions from Time Square to Carnegie Hall.
\end{itemize}

@@

\bibliographystyle{abbrv}
\bibliography{bibliography.bib} 
\end{document}

>>>>

\begin{itemize} \itemsep1pt \parskip0pt \parsep0pt
\item Google search for the population of Zimbabwe. 
\item On Youtube, find a video playing Bach's ``Ode to Joy.'' 
\item Find the Amazon best-sellers in ``Movies \& TV.''
\item On Yahoo, find the exchange rate of dollars to euros.
\item Find the Wikipedia ``History'' portal's featured article. 
\item On Twitter, find the currently trending topics.
\item On Bing Maps, find directions from Time Square to Carnegie Hall.
\end{itemize}

@@

\bibliographystyle{abbrv}
\bibliography{circumvention-experiment.bib} 
\end{document}
